Goal Recognition as Planning with Unknown Domain Models

### 2019-01-30 doc/ijcai-19-goalRecognition/goalRecognition.tex
first comments on goal recognition design added to the ijcai19 paper on goal recognition

\section{Classical planning with unknown domain models}
\label{sec:planning}
This section introduces a novel formulation for classical planning in a setting where no action model is given. This setting of classical planning is very related to the learning of action models for planning~\cite{SternJ17}. In particular it can be considered an extreme learning scenario when a model has to be learned from a single learning example that contains only two state observations, an initial state and the goals.

@@

>>>>

\section{Planning with unknown domain models}
\label{sec:planning}
This section introduces a novel formulation for classical planning in a setting where no action model is given. This setting of classical planning is very related to the learning of action models for planning~\cite{SternJ17}. In particular it can be considered an extreme learning scenario when a model has to be learned from a single learning example that contains only two state observations, an initial state and the goals.

@@

Planning with an unkown model is also related to {\em goal recognition design}~\cite{KerenGK14} where they compute the modification of the initial state that allow an efficient online goal recognition. Our approach is related since we are encoding the space of propositional schemas planning state variables, we encode at the initial state the {\em empty} actoin model with no preconditions and effects and provide actions to modify this model to enable the {\em goal recognition} process.
